IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-02 assets/channel_amplitude_100reflectors.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,3.397in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS}

@@

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,2.663in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.928in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.193in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/waveform_subband.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.481in,
at={(0.677in,3.374in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172701356454\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000255961727675924\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.036in,
height=0.481in,
at={(0.677in,2.645in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.19551151069007\\
2	2.79441682266723\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.76001760054032e-06\\
2	6.94107248595388e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.481in,
at={(0.677in,1.916in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00471916738670986\\
2	0.0113013795751173\\
3	0.0524973569625421\\
4	1.11631746294063\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.666856968017446\\
2	0.826759550766013\\
3	0.96159816303766\\
4	1.2653467150935\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.481in,
at={(0.677in,1.187in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000872616544376037\\
2	0.00117960004406015\\
3	0.00161605407069224\\
4	0.00228266132463128\\
5	0.00326342365821\\
6	0.00487936277124623\\
7	0.00881039674196349\\
8	0.0419634199055652\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633590459263079\\
2	0.785594177316295\\
3	0.891389674009387\\
4	0.98505471211105\\
5	1.05090474986801\\
6	1.10664902589546\\
7	1.1412268011736\\
8	1.16708811938208\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.481in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={  0, 0.4, 0.8},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000310341555926487\\
2	0.00035799764238\\
3	0.00041670813086453\\
4	0.000484920116868764\\
5	0.000569098471381299\\
6	0.000669877208860123\\
7	0.000793268903064817\\
8	0.000939331113982085\\
9	0.0011175247904389\\
10	0.00132972829292326\\
11	0.0015875351976808\\
12	0.00189182501786478\\
13	0.00226771472661325\\
14	0.00272021545715682\\
15	0.00331689397668614\\
16	0.00407528165955271\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.428729933737136\\
2	0.489701018897442\\
3	0.539263608495876\\
4	0.585347098517275\\
5	0.624083102405944\\
6	0.657759147074073\\
7	0.689461005203993\\
8	0.715900755845553\\
9	0.741047135425173\\
10	0.761923826165851\\
11	0.78165448191713\\
12	0.796874354752371\\
13	0.810144534289869\\
14	0.819572643230985\\
15	0.826293720140692\\
16	0.829491639456529\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,3.233in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213593413934\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000411418946938571\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,2.54in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.434593216761001\\
2	4.3899297145933\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.15579196934664e-05\\
2	1.1748417131072e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,1.846in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0143736245770149\\
2	0.0303952314208929\\
3	0.115397989725443\\
4	1.83286171599636\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.03274778152889\\
2	1.26444789136652\\
3	1.50497289223671\\
4	2.05482037288244\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,1.152in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00193817595567525\\
2	0.00257713054060487\\
3	0.00348488793501541\\
4	0.00488691757665795\\
5	0.00708186101407546\\
6	0.0115819776031387\\
7	0.0297619841444503\\
8	0.248823174288891\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.958056681914786\\
2	1.1753523246861\\
3	1.34398156020033\\
4	1.48468938243277\\
5	1.59662285127524\\
6	1.68382811164256\\
7	1.75299266281476\\
8	1.84970533450897\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000699803366708424\\
2	0.000800867722584431\\
3	0.000917767493119273\\
4	0.00105546869283256\\
5	0.0012213408897823\\
6	0.00141507752657299\\
7	0.00165144517333923\\
8	0.00193060125433753\\
9	0.00227670870277157\\
10	0.0027030187224025\\
11	0.00324897530466221\\
12	0.00397867693137808\\
13	0.00501781698344776\\
14	0.00655613193903264\\
15	0.009024934371904\\
16	0.0130872335381684\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.658945444448673\\
2	0.748750326986652\\
3	0.825803524447847\\
4	0.897209109075901\\
5	0.959520330551997\\
6	1.01644204271237\\
7	1.07098120306596\\
8	1.11834785156968\\
9	1.16491430867279\\
10	1.20444111502631\\
11	1.24260696441405\\
12	1.27263946826968\\
13	1.29990806955352\\
14	1.31826230888077\\
15	1.33150577776743\\
16	1.33694997002172\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
